### 2023-03-28 definitions.tex
details

Wqo admits many other equivalent formulations. For instance: 
$(X,\leq)$ is a wqo if and only if any infinite increasing sequence $U_0 \subseteq U_1 \subseteq U_2 \subseteq \cdots$ of
upward-closed subsets in $X$ eventually stabilizes, 
%      i.e. there is a $k \in N$ such that $U_k = U_{k+1} = U_{k+2} = \cdots $ 
if and only if any upward-closed subset $U \subseteq X$ has a
finite basis if and only if $(X,\leq)$ is well-founded (i.e. it admits no infinite strictly decreasing sequence) and without infinite antichains (i.e. there is no infinite subset in $X$ of mutually incomparable elements).
%
\iffalse
%

@@

In what follows, a downward closed set $D=\downarrow D$ is represented by its finite set of ideals $I_D=\{J_1, J_2,...,J_n\}$ satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ and that an upward closed set $U$ is represented by its finite set $Min_U$ of its minimal elements satisfying $U=\uparrow Min_U$.

Let $U,V$ be two upward-closed sets given by its set of minimal element and $D,E$ be two downward-closed sets given by its ideal decomposition. All the four  inclusions $U \subseteq V$,  $U \subseteq D$, $D \subseteq U$ and $D \subseteq E$ are decidable provided that the ordering is decidable.

>>>>

Wqo admits many other equivalent formulations. For instance: 
$(X,\leq)$ is a wqo if and only if any infinite increasing sequence $U_0 \subseteq U_1 \subseteq U_2 \subseteq \cdots$ of
upward-closed subsets in $X$ eventually stabilizes, 
%      i.e. there is a $k \in N$ such that $U_k = U_{k+1} = U_{k+2} = \cdots $ 
if and only if any upward-closed subset $U \subseteq X$ has a
finite basis if and only if $(X,\leq)$ is well-founded (i.e. it admits no infinite strictly decreasing sequence) and $X$ don't contain infinite subset of mutually incomparable elements (antichains).
%
\iffalse
%

@@

Quasi-orderings that have no infinite antichains enjoy a similar \emph{finite decomposition} property than wqo. In such \emph{Finite Antichains} sets $(X,\leq)$, every downward closed subset $D \subseteq X$ can be decomposed into a \emph{finite} set of ideals $J_i$ (an ideal is a directed downward closed subset): $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$.

In what follows, a downward closed set is represented by its finite set of ideals 
%		$D=\downarrow D$   $I_D=\{J_1, J_2,...,J_n\}$ 		satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ 
and an upward closed set $U$ is represented by its finite set minimal elements.
% $M_U$ of its  satisfying $U=\uparrow M_U$.

\alain{est-ce utile et correct ? Let $I,J$ be two upward-closed sets given by its set of minimal element and $D,E$ be two downward-closed sets given by its ideal decomposition. All the four  inclusions $U \subseteq V$,  $U \subseteq D$, $D \subseteq U$ and $D \subseteq E$ are decidable provided that the ordering is decidable.}
